\subsection{Cryptographic Primitives}

Many cryptographic systems, including Verificatum, make use of some
basic functions, normally called cryptographic primitives. These
primitives are functions or objects which possess properties
interesting in cryptographic contexts. Verificatum uses hash
functions, pseudo random generators and random oracles, all of which
are described in this chapter.

\subsubsection{Hash functions}
In general, a hash function is an easily computable function that
takes an input from an arbitrarily large input space and map it to an
element in a finite sized hash space \cite[p.~321]{hac}. As a consequence of this, there
will exist several inputs which map to the same hash. Hash functions
are used in many different areas of computer science and there are
many different kinds tailored to have the properties desired for its
particular application. A cryptographic hash function is a hash
function with two important properties. First, the hashes are
uniformly distributed in the hash space. Simply put, this means that
if you try to guess which hash a given input will produce you will
never have a significantly better chance than just random
guessing. Furthermore, for a cryptographic hash function all of the
following are infeasible.

\begin{itemize}
\item Find an input which produces a given hash.
\item Given an input and its hash, find another input with the same hash.
\item Find two inputs which produce the same hash.
\end{itemize}

In mix-nets any cryptographic hash function could be used. A
common choice is the SHA-2 family of hash functions, namely SHA-256,
SHA-384 and SHA-512. Their main difference is the number of bits they
output, i.e. the size of the hash space which is 256, 384 and 512
respectively.

\subsubsection{Pseudo Random Generators}

A \emph{Pseudo Random Generator}, PRG, is a function which takes an
initial seed and expands it into a longer sequence of seemingly random
data \cite[p.~170]{hac}. The output is random in the sense that it should be
indistinguishable from truly random output but the same seed will
always produce the same output.

The Verificatum mix-net uses a PRG based on a cryptographic hash
function that hashes the seed together with a counter which increases
for every iteration.

\subsubsection{Random Oracles}

In theory, a \emph{Random Oracle}, RO, is a black box which takes an
input and returns a truly random output from its output space
\cite{oracle}. It will always respond with the same output for the
same input. This is very similar to a hash function but has some
subtle differences. An RO is a purely theoretical construct which
defines no actual function, only a relationship between inputs and
outputs.

In practice though, we use a construct within the Verificatum mix-net
which we call an RO. This construct is based on a cryptographic hash
function and a seed. The purpose of the seed is to permute the
relationship between the inputs and outputs of the hash function and
thus creating an easily randomizable RO without coming up with a whole
new hash function.
