\section{Results}

\subsection{Resulting Code}

Our resulting implementation of the mix-net consists of about 5500
lines of C++ code divided into three parts, Arithmetic, Crypto and
Verifier. The first two parts are the byte tree classes and the
cryptographic primitives respectively. The Verifier part contains the
actual verification algorithms.

The code is available on GitHub\cite{github} but should not be
considered a stable release.


\subsection{Comments on the Documentation}

The overall impression of the documentation was that it contained all
information needed to implement the verifier. There were, however,
errors affecting the execution of the verifier. Some of the problems
arising from these errors were overcome after discussion with
Wikström. See Appendix B for a list of errors found and specific
comments about the report.

In the absolute beginning of the document, the reader is thrown into
details about the zero-knowledge proofs used in VMN. A more gentle
approach would be to introduce the VMN without assuming too much
acquaintance with it or provide the means for the reader to do so on
his or her own. It would also be appreciated if the document contained
a description of Pedersen commitments.

The background, including a description of a mix-net based on the El
Gamal cryptosystem, is clear and concise. After the background, the
document contains a list of manageable subtasks in order to facilitate
implementation. This list was greatly appreciated as it gave someone
unacquainted with VMN ideas of suitable starting points.

Chapters 4 through 6 contain necessary and easily accessible
information. However, chapter 4 on byte trees and chapter 6 on
representation of arithmetic objects are closely related and could
advantageously be presented together while bringing up the
cryptographic primitives of chapter 5 afterwards. The part on deriving
group elements from random strings depends on chapter 5 and
consequently needs to be presented thereafter. See Appendix C for a
clarification on these comments.

Chapter 6.6 on Marshalling Groups contains specific details regarding
the Verificatum software with strong connections to Java. This chapter
could be rephrased to only include information actually needed for
implementation of a verifier.

Lastly, the chapter on verification of Fiat-Shamir proofs relies
heavily on the derivation of group elements from random strings. By
moving chapter 7 to right before the chapter on cryptographic
primitives, usage of the document will probably demand less page
turns.

\section{Conclusion}
The use of mix-nets in electronic voting brings with it many
advantages but also several risks. It is important that voters feel
confident and safe about voting, because otherwise the voting system
has lost its purpose. The creation of verifiable mix-nets speaks in
favour for electronic voting.

The evaluation and improvement of the VMN verifier document is
important in order to allow third parties to independetly verify
correct execution of the mix-net. By implementing a verifier, several
errors could be corrected and suggestions regarding the document's
structure could be made.

The implementation and code creation of the verifer would have been
simplified by defining more layers of abstractions in the code
structure. Specifically, some classes representing various
mathematical objects, such as group elements, would have made the code
easier to maintain. We believe that a more solid understanding of the
structure of VMN before we started programming would have helped in
creating a better structure of the verifier. The choices of third
party libraries were good and they were all easy to use in our
project. This also makes the amount of code which need to be written
smaller. The lack of test data greatly increased the difficulty of
implementing the verifier.

The specification document for the verifier does include all the
information required to write the verifier. However, the structure
could be improved for greater readability. There is also some
unnecessary information in the document. Lastly, the document could
benefit from an improved description of the VMN so that one easier can
acquire a better understanding of what approach to take when
implementing the verifier.
